---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Making correct information unit scoring slightly less painful\*

<!-- badges: start -->

<!-- badges: end -->

The goal of this shiny app is to make CIU scoring faster, easier, and more reliable.

You can run the app from R on your computer by using the following code (note, this will automatically install any needed packages). Don't worry if you are new to R, the app should run automatically with these three commands. Here's a helpful resource for getting started: <https://rstudio-education.github.io/hopr/starting.html>. You should not need Rstudio.

```{r cars, eval=F}
# not run
install.packages('shiny')
library(shiny)
shiny::runGitHub('rbcavanaugh/ciu_analysis', subdir = 'rungithub', launch)
```

#### [Or just access it at shinyapps.io!](https://rb-cavanaugh.shinyapps.io/aphasia-ciu/)

### Find information about CIUs:

<https://pubs.asha.org/doi/abs/10.1044/jshr.3602.338>

<https://pubs.asha.org/doi/abs/10.1044/jshr.3702.399>

<https://scholar.google.com/scholar?hl=en&as_sdt=0%2C39&q=correct+information+unit+Nicholas+brookshire&btnG=>

\*not to be construed as strong support for CIUs as a measure of discourse
